---
title: "Logistic Regression on Titanic Data"
output:
  html_document:
    toc: yes
    toc_float: yes
---
This documents narrates the analysis of Titanic survival data.  

Packages that will be used in this analysis: 
```{r message=FALSE, warning = FALSE}
library(magrittr)
library(dplyr)
library(ggplot2)
library(titanic)
```


# Wrangling

## Load  
Import the data provided by the titanic package
```{r }
ds0 <- titanic::titanic_train
head(ds0)
dplyr::glimpse(ds0)
```

## Inspect  
To better understand the data set, let us inspect quantitative properties of each variable
```{r }
explore::describe_all(ds0)

```

## Tweek 
To prepare our data for modeling, let perform routine data transformations:  
 * 1. Convert column names to lowercase  
 * 2. Select and sort columns
 * 3. Rename columns  
 * 4. Covert strings to factors  
 * 5. Filter out missing values  
```{r tweek-data}
# create a new copy that will store tweeks
ds1 <- ds0
# 1. convert columns names to lowercase
names(ds1) <- tolower(names(ds1))
# ds1 %>% glimpse()
# 2. Keep only specific variables and sort columns 
ds1 <- ds1 %>% 
  dplyr::select(survived, pclass, sex, age, sibsp, parch, fare, embarked)
# ds1 %>% glimpse()
# 3. Rename variables
ds1 <- ds1 %>% 
  dplyr::rename(
    n_siblings_spouses  = sibsp
    ,n_parents_children = parch
    ,price_ticket       = fare
    ,port_embarked      = embarked
  )
# 4. Convert a character variable to a factor
ds1 <- ds1 %>% 
  dplyr::mutate(
    survived = factor(survived, levels = c(0,1), labels = c("Died", "Survived"))
    ,sex     = factor(sex, levels = c("male","female"), labels = c("Men","Women"))
    ,pclass  = factor(pclass, levels = c(1,2,3), labels = c("First","Second", "Third"))
  )
# 5. Remove observations where a) age is NA b) port_embarked is missing ("")
ds1 <- ds1 %>% 
  dplyr::filter(!is.na(age)) %>% 
  dplyr::filter(port_embarked != "")
# create an alias data set for modeling
ds_modeling <- ds1
ds_modeling %>% glimpse()
```


# Tabulating

Summary tables to help us see observed differenced broken down by levels of predictors

```{r basic-tables}
#  How does survival brake down by levels of predictors?
ds_modeling %>% 
  dplyr::group_by(survived, sex) %>% 
  dplyr::summarize(
    n_people = n()
    ,mean_age = mean(age, na.rm = T)
  )
```

# Modeling

## 0 - Sex

### Summary
```{r}
model_0 <- stats::glm(
  formula = survived ~ sex
  ,family = "binomial"
  ,data = ds_modeling
)
summary(model_0)
# create levels of predictors for which to generate predicted values
ds_predicted_0 <- ds_modeling %>% 
  dplyr::select(sex) %>% 
  dplyr::distinct()
# add model prediction
ds_predicted_0 <- ds_predicted_0 %>% 
  dplyr::mutate(
    log_odds = predict(object = model_0, newdata = .)
    ,probability = plogis(log_odds)
  )
# ds_predicted_0
```

### Graph - g0

```{r}
ds_predicted_0 %>% 
  ggplot(aes(x = sex, y = probability))+
  geom_bar(stat = "identity")
```

## 1 - Sex + Age

### Summary (g1)
```{r}
model_1 <- stats::glm(
  formula = survived ~ sex + age
  ,family = "binomial"
  ,data = ds_modeling
)
summary(model_1)
# create levels of predictors for which to generate predicted values
ds_predicted_1 <- ds_modeling %>% 
  dplyr::select(sex, age) %>% 
  dplyr::distinct()
# add model prediction
ds_predicted_1 <- ds_predicted_1 %>% 
  dplyr::mutate(
    log_odds     = predict(object = model_1, newdata = .)
    ,probability = plogis(log_odds)
  )
# ds_predicted_1
```

### Graph (g1)

```{r}
g1 <- ds_predicted_1 %>% 
  ggplot(aes(x = age, y = probability))+
  geom_point(aes(color = sex))
g1
```


## 2 - Sex + Age + Class


### Summary (m2)
```{r}
model_2 <- stats::glm(
  formula = survived ~ sex + age + pclass
  ,family = "binomial"
  ,data = ds_modeling
)
summary(model_2)
# create levels of predictors for which to generate predicted values
ds_predicted_2 <- ds_modeling %>% 
  dplyr::select(sex, age, pclass) %>% 
  dplyr::distinct()
# add model prediction
ds_predicted_2 <- ds_predicted_2 %>% 
  dplyr::mutate(
    log_odds     = predict(object = model_2, newdata = .)
    ,probability = plogis(log_odds)
  )
# ds_predicted_2
```

### Graph (g2)
```{r}
g2 <- ds_predicted_2 %>% 
  ggplot(aes(x = age, y = probability))+
  geom_point(aes(color = sex))+
  facet_wrap("pclass")
g2
```


## 3 - Sex + Age + Class + Port

### Summary (m3)
```{r}
model_3 <- stats::glm(
  formula = survived ~ sex + age + pclass + port_embarked
  ,family = "binomial"
  ,data = ds_modeling
)
summary(model_3)
# create levels of predictors for which to generate predicted values
ds_predicted_3 <- ds_modeling %>% 
  dplyr::select(sex, age, pclass, port_embarked) %>% 
  dplyr::distinct()
# add model prediction
ds_predicted_3 <- ds_predicted_3 %>% 
  dplyr::mutate(
    log_odds     = predict(object = model_3, newdata = .)
    ,probability = plogis(log_odds)
  )
# ds_predicted_3

```

### Graph (g3)
```{r}
g3 <- ds_predicted_3 %>% 
  ggplot(aes(x = age, y = probability))+
  geom_point(aes(color = sex, shape = port_embarked))+
  facet_grid(. ~ pclass)
  # facet_grid(port_embarked ~ pclass)
g3
```




